---
title: "Homework-1 (Group 5)"
author: "Naren Mohan, Srujana Gaddam, Simran Bhatia"
date: "9/22/2021"
output: html_document
---
### Including the libraries
  ```{r echo=TRUE, message=FALSE}
library(readr)
library(dplyr)
library(stringr)
```


### Reading the Farmers Market Dataset
```{r eval=TRUE, echo=TRUE}
df_fm <- read_csv("fm.csv", col_types = cols(Season3Date = col_character(), 
    Season3Time = col_character(), Season4Date = col_character(), 
    Season4Time = col_character()))
```

### 1.1 (10 points) Compute the number of farmers market in the United States
```{r eval=TRUE, echo=TRUE}
fm_count <- length(unique(df_fm$FMID))
cat("Total number of Farmers Market in the United States:", fm_count)
```

### 1.2 (10 Points) Write a code to compute the number of farmers markets by state and arrange them in descending order of number of farmers market.
```{r eval=TRUE, echo=TRUE}

# by_state <- df_fm %>% 
#   group_by(State) %>%
#   summarise(fm_count = n()) %>%
#   arrange(-fm_count)
# print(by_state)

# Creating an empty data frame
by_state = data.frame(state=character(), farmer_market_count=integer())

for(i in 1:length(df_fm$State)) {
  if(!(df_fm$State[i] %in% by_state$state)) {
    by_state <- rbind(by_state, data.frame(state=df_fm$State[i], farmer_market_count=1))
  }
  else{
    state_index <- which(by_state$state == df_fm$State[i])
    by_state$farmer_market_count[state_index] <- by_state$farmer_market_count[state_index] + 1
  }
}

# Sorting it in descending order
by_state <- by_state %>%
  arrange(-farmer_market_count)

print(by_state)

```


### 1.3 (10 Points) Write a code to compute the number of farmers market by cities in Massachusetts and display the top five cities.
```{r eval=TRUE, echo=TRUE}
# Filtering the farmers market in Massachusetts 
df_fm_mass <- df_fm %>% 
  filter(State == "Massachusetts")

by_city = data.frame(city=character(), farmer_market_count=integer())
for(i in 1:length(df_fm_mass$city)) {
  if(!(df_fm_mass$city[i] %in% by_city$city)) {
    by_city <- rbind(by_city, data.frame(city=df_fm_mass$city[i], farmer_market_count=1))
  }
  else {
    city_index <- which(by_city$city == df_fm_mass$city[i])
    by_city$farmer_market_count[city_index] <- by_city$farmer_market_count[city_index] + 1
  }
}

by_city <- by_city %>%
  arrange(-farmer_market_count)

print(head(by_city, 5))
```

### 1.4 (10 Points) Write a code to show the top 5 states by number of farmers market that offers coffee
```{r eval=TRUE, echo=TRUE}
# Checking for different data entries
# print(unique(df_fm["Coffee"]))

# Cleaning the entries in the "Coffee column"
# Marking the NA entries as "N" for Coffee production
index_na <- is.na(df_fm["Coffee"])
df_fm["Coffee"][index_na] <- "N"

# Verifying
# print(unique(df_fm["Coffee"]))

df_fm_coffee <- df_fm %>%
  filter(Coffee == "Y") %>%
  group_by(State) %>%
  summarise(fm_count_coffee = n()) %>%
  arrange(-fm_count_coffee)

print(head(df_fm_coffee, 5))
```

### Reading the Wine Dataset
```{r eval=TRUE, echo=TRUE, message=FALSE}
# Reading the dataset 
df_wine <- read_csv("wine_data.csv")
```
### 2.1 (20 points) Use the “designation” variable and calculate the number of 20 year old wine in the dataset
```{r eval=TRUE, echo=TRUE}
wd <- df_wine %>% 
  mutate(lc_designation = str_to_lower(df_wine$designation))
wd_20 <- wd %>% 
  filter(str_detect(lc_designation, '20 year|20 yr|20 ano|20-year'))

cat("Number of 20 year old wine:", dim(wd_20)[1])
```

### Reading the Keyword Dataset
```{r eval=TRUE, echo=TRUE, message=FALSE}
# Reading the dataset
df_keyword <- read_csv("Keyword_data - Keyword_data.csv")
```
### 3.1 (40 points) Create a KCN network from a sample data
```{r eval=TRUE, echo=TRUE}
# Cleaning the rows
df_kw <- df_keyword[!(is.na(df_keyword$Title) | (nchar(df_keyword$Title) < 8)), ]

# Getting all the unique keywords
unq_vec <- character()
for(i in 2:dim(df_kw)[2]) {
  temp <- df_kw[[i]]
  unq_vec <- c(unq_vec, temp)
}

unq_vec <- unq_vec %>%
  unique()

unq_vec <- sort(unq_vec[!is.na(unq_vec)])

df_kw2 <- df_kw[, 2:dim(df_kw)[2]]

# Creating a data frame with unique keywords
df_matrix <- data.frame(row.names = unq_vec)
for(i in 1:length(unq_vec)) {
  df_matrix[unq_vec[i]] <- integer(length(unq_vec))
}

for(i in 1:dim(df_kw2)[1]) {
  keywords_row <-  as.character(as.vector(df_kw2[i, ]))
  for(j in 1:length(keywords_row)) {
    temp1 <- keywords_row[j]
    for(k in 1:length(keywords_row)) {
      if(is.na(keywords_row[k]) | is.na(temp1)) {
        # Do nothing
      } else if(temp1 == keywords_row[k]) {
        # Do nothing
      } else {
        df_matrix[temp1, keywords_row[k]] <- df_matrix[temp1, keywords_row[k]] + 1
      }
    }
  }
}

print(df_matrix)
```

