---
title: "IE 5374- Sec 1- Group 5- Project 2"
author: "Naren, Simran, Srujana"
output: html_document
---
# Assignment Objective
The objective of project 2 is to perform keyword network analysis and word frequency analysis.

# Libraries
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(lubridate)
library(tidytext)
library(ggplot2)
library(tidyr)
library(igraph)
library(ggraph)
library(qdap)
library(tm)
```

# Data
```{r message=FALSE, warning=FALSE}
keywordData <- read_csv("../HW 1/Keyword_data - Keyword_data.csv")
tweets2017 <- read_csv("./2017.csv", col_select=c("date", "tweet"))
tweets2021 <- read_csv("./2021.csv", col_select = c("date", "tweet"))
```

# Task 1
## Task 1.1
Use the solution from homework 1 question 3.1 as the adjacency matrix

```{r Task 1.1}
# Cleaning the rows
df_kw <- keywordData[!(is.na(keywordData$Title) | (nchar(keywordData$Title) < 8)), ]

# Getting all the unique keywords
unq_vec <- character()
for(i in 2:dim(df_kw)[2]) {
  temp <- df_kw[[i]]
  unq_vec <- c(unq_vec, temp)
}

unq_vec <- unq_vec %>%
  unique()

unq_vec <- sort(unq_vec[!is.na(unq_vec)])

df_kw2 <- df_kw[, 2:dim(df_kw)[2]]

# Creating a data frame with unique keywords
matrix_kw <- data.frame(row.names = unq_vec)
for(i in 1:length(unq_vec)) {
  matrix_kw[unq_vec[i]] <- integer(length(unq_vec))
}

for(i in 1:dim(df_kw2)[1]) {
  keywords_row <-  as.character(as.vector(df_kw2[i, ]))
  for(j in 1:length(keywords_row)) {
    temp1 <- keywords_row[j]
    for(k in 1:length(keywords_row)) {
      if(is.na(keywords_row[k]) | is.na(temp1)) {
        # Do nothing
      } else if(temp1 == keywords_row[k]) {
        # Do nothing
      } else {
        matrix_kw[temp1, keywords_row[k]] <- matrix_kw[temp1, keywords_row[k]] + 1
      }
    }
  }
}

print(matrix_kw)
```

## Task 1.2
Read the adjacency matrix and convert it into a weighted network

```{r Task 1.2}
matrix_kw <- as.matrix(matrix_kw)
net <- graph_from_adjacency_matrix(matrix_kw,
                                   mode="undirected",
                                   weighted=TRUE)
```

## Task 1.3
Compute node degree and strength

```{r Task 1.3}
strength_kw <- strength(net)

degree_kw <- degree(net)
```

## Task 1.4
Show the top 10 nodes by degree and top 10 nodes by strength

```{r Task 1.4}
# arranging both lists in descending order
strength_kw <- sort(strength_kw, decreasing = TRUE)
degree_kw <- sort(degree_kw, decreasing = TRUE)

# top 10 nodes by degree
degree_kw[1:10]

# top 10 nodes by strength
strength_kw[1:10]
```

## Task 1.5
Show the top 10 node pairs by weight

```{r Task 1.5}
edges <- E(net)
edge_list <- as.data.frame(cbind(get.edgelist(net), edges$weight))
colnames(edge_list) <- c("Vertex 1", "Vertex 2", "Weight")
edge_list$Weight <- as.integer(edge_list$Weight)
edge_list <- edge_list[order(-edge_list$Weight), ]
edge_list[1:10, ]
```

##Task 1.6
Plot average strength on y-axis and degree on x-axis

```{r Task 1.6}
# getting degrees in dataframe form
df_degree_kw <- data.frame(keyName=names(degree_kw), value=degree_kw, row.names=NULL)

# getting strengths in dataframe form
df_strength_kw <- data.frame(keyName=names(strength_kw), value=strength_kw, row.names=NULL)

# joining degree and strength dataframes
df_kw3 <- left_join(df_degree_kw, df_strength_kw, by="keyName")

# calculating average degree and strength
df_kw3 <- df_kw3 %>%
  mutate(avgStrength = `value.y`/`value.x`)

# plotting average degree against average strength
plot <- ggplot(df_kw3, aes(x=`value.x`, y=avgStrength, color=avgStrength)) +
  geom_point(size = 3) +
  labs(title = "Degree v/s Average Strength of Keyword Vertices",
       x = "Degree",
       y = "Average Strength") +
  scale_color_gradient(low="#F2789F", high="#F999B7") +
  theme_minimal() +
  guides(color = "none")

plot
  
```

# Task 2
The link provides the twitter data of Elon Musk from 2010-2021. For analysis consider the years 2017-2021. Each year has thousands of tweets. Assume each year to be a document (all the tweets in one year will be considered as a document).

## Reading the dataset from 2017 to 2021

```{r Task 2.0}
tweets2017 <- tweets2017 %>%
  filter(date >= as.Date("2017-01-01"))

tweets2021 <- tweets2021 %>%
  mutate(date = as.Date(date))

tweets2018 <- tweets2021 %>%
  filter(date >= as.Date("2018-01-01") & date < as.Date("2019-01-01"))
tweets2019 <- tweets2021 %>%
  filter(date >= as.Date("2019-01-01") & date < as.Date("2020-01-01"))
tweets2020 <- tweets2021 %>%
  filter(date >= as.Date("2020-01-01") & date < as.Date("2021-01-01"))
tweets2021 <- tweets2021 %>%
  filter(date >= as.Date("2021-01-01") & date < as.Date("2022-01-01"))
```

## Task 2.1
Compute word frequencies for each year. Exclude the stop words

```{r Task 2.1}
# function to exclude stop words and compute word frequencies

getWordFrequencies <- function(tweetyear) {
    # Remove Stop words
  filtyear <- rm_stopwords(tweetyear$tweet, stopwords=Top200Words, strip=TRUE, ignore.case=TRUE,
                          apostrophe.remove=TRUE, separate = FALSE)
  
  #Get all the words into one single string
  stryear <- ""
  for(i in 1:length(filtyear)){
    stryear <- paste(stryear, filtyear[i])
  }
  
  stoppo <- c("amp", "httpstco")
  stryear <- rm_stopwords(stryear, stopwords=stoppo, strip=TRUE, ignore.case=TRUE,
                          apostrophe.remove=TRUE, separate = FALSE)
  
  str1 <- strsplit(stryear, split=" ")
  str1.freq<-table(unlist(str1))
  
  df1 <- data.frame(cbind(word = names(str1.freq), freq = as.integer(str1.freq)))
  df1$freq <- as.integer(df1$freq)
  df1 <- df1[order(df1$freq, decreasing = TRUE), ]
  
  return(df1)
}
```

### Task 2.1a - 2017
```{r Task 2.1a}
wordFrequencies2017 <- getWordFrequencies(tweets2017)
```

### Task 2.1b - 2018
```{r Task 2.1b}
wordFrequencies2018 <- getWordFrequencies(tweets2018)
```

### Task 2.1c - 2019
```{r Task 2.1c}
wordFrequencies2019 <- getWordFrequencies(tweets2019)
```

### Task 2.1d - 2020
```{r Task 2.1d}
wordFrequencies2020 <- getWordFrequencies(tweets2020)
```

### Task 2.1e - 2021
```{r Task 2.1e}
wordFrequencies2021 <- getWordFrequencies(tweets2021)
```

## Task 2.2
Show top 10 words (for each year) by the highest value of word frequency

### Task 2.2a - 2017
```{r Task 2.2a}
wordFrequencies2017 %>%
  top_n(10)
```

### Task 2.2b - 2018
```{r Task 2.2b}
wordFrequencies2018 %>%
  top_n(10)
```

### Task 2.2c - 2019
```{r Task 2.2c}
wordFrequencies2019 %>%
  top_n(10)
```

### Task 2.2d - 2020
```{r Task 2.2d}
wordFrequencies2020 %>%
  top_n(10)
```

### Task 2.2e - 2021
```{r Task 2.2e}
wordFrequencies2021 %>%
  top_n(10)
```

## Task 2.3
Plot histogram of word frequencies for each year

```{r Task 2.3}
# function to plot histogram of word frequencies

plotHist <- function(wordfrequency) {
    plot1 <- ggplot(wordfrequency[1:10, ], aes(x= reorder(word, -freq), y = freq, fill="#F2789F")) +
    geom_col() +
    labs(title="Histogram",
           x = "Word",
           y = "Frequency") +
      theme_minimal() +
      guides(color = "none", fill = "none")
  
  print(plot1)
}
```

### Task 2.3a - 2017
```{r Task 2.3a}
plotHist(wordFrequencies2017)
```

### Task 2.3b - 2018
```{r Task 2.3b}
plotHist(wordFrequencies2018)
```

### Task 2.3c - 2019
```{r Task 2.3c}
plotHist(wordFrequencies2019)
```

### Task 2.3d - 2020
```{r Task 2.3d}
plotHist(wordFrequencies2020)
```

### Task 2.3e - 2021
```{r Task 2.3e}
plotHist(wordFrequencies2021)
```

## Task 2.4
Use Zipf’s law and plot log-log plots of word frequencies and rank for each year

```{r Task 2.4}
# function to use zipf's law and plot log-log plots

plotLogLog <- function(wordfrequency) {
    wordfrequency$rank <- dim(wordfrequency)[1] + 1 - row_number(wordfrequency$freq)
    n <- sum(wordfrequency$freq)
    
    wordfrequency$tf <- wordfrequency$freq / n
    
    plot2 <- wordfrequency %>%
      ggplot(aes(rank, tf)) +
      geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE, color="#F2789F") +
      scale_x_log10() +
      scale_y_log10() +
      labs(title="Log-log plots", x="Rank", y="Word Frequency") +
      theme_minimal() +
      guides(color = "none")
    
    print(plot2)
}
```

### Task 2.4a - 2017

```{r Task 2.4a}
plotLogLog(wordFrequencies2017)
```

### Task 2.4b - 2018
```{r Task 2.4b}
plotLogLog(wordFrequencies2018)
```

### Task 2.4c - 2019
```{r Task 2.4c}
plotLogLog(wordFrequencies2019)
```

### Task 2.4d - 2020
```{r Task 2.4d}
plotLogLog(wordFrequencies2020)
```

### Task 2.4e - 2021
```{r Task 2.4e}
plotLogLog(wordFrequencies2021)
```

## Task 2.5
Create bigram network graphs for each year

```{r Task 2.5}
# function to create bigram network

createBigramNet <- function(tweetyear) {
  filtyear <- rm_stopwords(tweetyear$tweet, stopwords=Top200Words, strip=T, ignore.case=T, apostrophe.remove=T, separate=F)
  
  df1_bigrams <- tibble(txt = filtyear) %>%
    unnest_tokens(bigram, txt, token = "ngrams", n = 2)
  
  df1_bigrams <- as.data.frame(df1_bigrams)
  df1_bigrams.freq <- table(df1_bigrams)
  
  df2 <- data.frame(cbind(bigram = names(df1_bigrams.freq), freq = as.integer(df1_bigrams.freq)))
  df2$freq <- as.integer(df2$freq)
  df2 <- df2[order(df2$freq, decreasing = TRUE), ]
  df2 <- df2 %>%
    separate(bigram, c("word1", "word2"), sep = " ")
  
  df2_graph <- df2 %>%
    filter(freq > 8) %>%
    graph_from_data_frame()
  
  ggraph(df2_graph, layout = "fr") +
    geom_edge_link() +
    geom_node_point() +
    geom_node_text(aes(label = name, color="#F2789F"), vjust = 1, hjust = 1) +
    theme_minimal() +
    guides(color = "none")
}
```

### Task 2.5a - 2018

```{r Task 2.5a}
createBigramNet(tweets2017)
```

### Task 2.5b - 2018

```{r Task 2.5b}
createBigramNet(tweets2018)
```

### Task 2.5c - 2019

```{r Task 2.5c}
createBigramNet(tweets2019)
```

### Task 2.5d - 2020

```{r Task 2.5d}
createBigramNet(tweets2020)
```

### Task 2.5e - 2021

```{r Task 2.5e}
createBigramNet(tweets2021)
```